---
title: "Technical Description"
output: html_document
---

```{r setup, include=FALSE}
if(!require(mlbench)){install.packages("mlbench"); require(mlbench)} 
if(!require(tidyverse)){install.packages("tidyverse"); library(tidyverse)} 
if(!require(modelr)){install.packages("modelr"); library(modelr)} 
if(!require(ModelMetrics)){install.packages("ModelMetrics"); require(ModelMetrics)}
if(!require(recipes)){install.packages("recipes"); require(recipes)}
if(!require(DEoptimR)){install.packages("DEoptimR"); require(DEoptimR)}
if(!require(caret)){install.packages("caret"); require(caret)}
if(!require(dplyr)){install.packages("dplyr"); require(dplyr)}
if(!require(gam)){install.packages("gam"); require(gam)} 
if(!require(prophet)){install.packages("prophet"); require(prophet)} 
if(!require(plotly)){install.packages("plotly"); require(plotly)} 
if(!require(shinycssloaders)){install.packages("shinycssloaders"); require(shinycssloaders)} 
if(!require(plyr)){install.packages("plyr"); require(plyr)} 
if(!require(shinyWidgets)){install.packages("shinyWidgets"); require(shinyWidgets)} 
```

# Read our Technical Desciption in the following link. 
# View our code below.
https://docs.google.com/a/uw.edu/document/d/1gOuzRaODkoJyqCE7FUwQZqj3UbQ9KmR1fhXqL2XVQ3s/edit?usp=sharing


### Downloading and Cleaning the Data

The following code works with files that were too large to upload to Github. After cleaning them, we created CSV's that were of smaller size that we work with for our models.

```{r, eval=FALSE}
##### Downloading the data (files too big to upload to Github )
ParcelData <- read_csv("./data/EXTR_Parcel.csv")   

AppraisedVal <- read_csv("./data/EXTR_RPAcct_NoName.csv")

#####This dataset contains parcel info and zip code
parcel.Info <- ParcelData %>% filter(DistrictName == 'SEATTLE')   

parcel.Info$PIN <- paste(parcel.Info$Major, parcel.Info$Minor, sep="")   

parcel.Info <- parcel.Info %>% select(PIN, CurrentZoning, SqFtLot)  

#####This dataset contains appraised value per parcel
appraised.info <- AppraisedVal %>% filter(CityState == 'SEATTLE WA') %>% select(AcctNbr, ZipCode, CityState, BillYr, ApprLandVal)   
colnames(appraised.info)[colnames(appraised.info) == 'AcctNbr'] <- 'id'

##### Downloading parcel data from allof Seattle
MHADataOne <- read_csv("~/Documents/INFO_370/Final/MHADataOne.csv")   

MHADataTwo <- read_csv("~/Documents/INFO_370/MHADataTwo.csv")   

MHADataThree <- read_csv("~/Documents/INFO_370/Final/MHADataThree.csv")   

MHADataFour <- read_csv("~/Documents/INFO_370/Final/MHADataFour.csv")

##### Selecting Columns that matter to us
MHADataFour <- MHADataFour %>% select(PIN, SITETYPE, ADDR_FULL, FULLNAME, ZIP5, LOTSQFT, LAT, LON, APPRLNDVAL, APPR_IMPR, ZONING, Existing_Z, MHA_ZONING, MHA_TIER_F)   

MHADataThree <- MHADataThree %>% select(PIN, SITETYPE, ADDR_FULL, FULLNAME, ZIP5, LOTSQFT, LAT, LON, APPRLNDVAL, APPR_IMPR, ZONING, Existing_Z, MHA_ZONING, MHA_TIER_F)   

MHADataTwo <- MHADataTwo %>% select(PIN, SITETYPE, ADDR_FULL, FULLNAME, ZIP5, LOTSQFT, LAT, LON, APPRLNDVAL, APPR_IMPR, ZONING, Existing_Z, MHA_ZONING, MHA_TIER_F)   

MHADataOne <- MHADataOne %>% select(PIN, SITETYPE, ADDR_FULL, FULLNAME, ZIP5, LOTSQFT, LAT, LON, APPRLNDVAL, APPR_IMPR, ZONING, Existing_Z, MHA_ZONING, MHA_TIER_F)

##### Combining data into one large data frame
total <- merge(MHADataThree,parcel.Info ,by="PIN")   

total2 <- merge(MHADataTwo,parcel.Info ,by="PIN")   

total3 <- merge(MHADataOne,parcel.Info ,by="PIN")   

total4 <- merge(MHADataFour,parcel.Info ,by="PIN")   


total.no.years <- rbind(total,total2, total3, total4)   

write.csv(total.no.years, file = "finalDataNoYears.csv")   

total.no.years <- read.csv("finalDataNoYears.csv")

##### Downloading and selecting columns for Appraisal data
appraisal.data <- read_csv("~/Downloads/EXTR_RealPropApplHist_V.csv")   

appraisal.data <- appraisal.data %>% filter(RollYr == '2013' | RollYr == '2014' | RollYr == '2015' | RollYr == '2016' | RollYr == '2017')   

appraisal.data$PIN <- paste(appraisal.data$Major, appraisal.data$Minor, sep="")   

appraisal.data <- appraisal.data %>% select(PIN, RollYr, LandVal, ImpsVal, UpdateDate)   

appraisal.data <- appraisal.data %>% mutate(TotalVal = as.numeric(LandVal) + as.numeric(ImpsVal))

##### combining all the data into one 
newTotal <- merge(total,appraisal.data ,by="PIN")   

newTotal2 <- merge(total2,appraisal.data ,by="PIN")   

newTotal3 <- merge(total3,appraisal.data ,by="PIN")   

newTotal4 <- merge(total4,appraisal.data ,by="PIN")


##### One dataset with all the data we will be using from 2013 - 2017
all.data <- rbind(newTotal, newTotal2, newTotal3, newTotal4)   

write.csv(all.data, file = "dataYears13to17.csv")   

all.data <- read.csv('dataYears13to17.csv')

##### Cleaning the data
all.data <- all.data[!(is.na(all.data$ADDR_FULL)), ]   

all.data <- all.data[!(is.na(all.data$Existing_Z)), ]   

all.data <- all.data[!(is.na(all.data$ZONING)), ]


##### Neighborhood Data
NeighboOne <- read_csv("./data/MHA2part1.csv")   

NeighboTwo <- read_csv("./data/MHA2part2.csv")   

NeighboThree <- read_csv("./data/MHA2part3.csv")   

NeighboFour <- read_csv("./data/MHA2part4.csv")

NeighboOne <- NeighboOne %>% filter(LEVY_JURIS == 'SEATTLE')   

NeighboTwo <- NeighboTwo %>% filter(LEVY_JURIS == 'SEATTLE')   

NeighboThree <- NeighboThree %>% filter(LEVY_JURIS == 'SEATTLE')   

NeighboFour <- NeighboFour %>% filter(LEVY_JURIS == 'SEATTLE')

##### combining and cleaning neighborhood data
all.neighborhood <- rbind(NeighboOne, NeighboTwo, NeighboThree, NeighboFour)   

all.neighborhood <- all.neighborhood %>% select(PIN, UV_NAME)   

all.neighborhood <- na.omit(all.neighborhood)   


##### all the data with neighborhood information included
neighborhood.all.data <- merge(all.neighborhood, all.data ,by="PIN")   



##### Data with older amounts of years that we will use to train and test our forecasting model
appraisal.data <- read_csv("~/Downloads/EXTR_RealPropApplHist_V.csv")   

appraisal.data$PIN <- paste(appraisal.data$Major, appraisal.data$Minor, sep="")   

appraisal.data <- appraisal.data %>% select(PIN, RollYr, LandVal, ImpsVal, UpdateDate)   

appraisal.data$RollYr <- as.numeric(appraisal.data$RollYr)   

old.years <- appraisal.data %>% filter(RollYr == '2000' | RollYr == '2001' | RollYr == '2002' | RollYr == '2003' | RollYr == '2004' |  RollYr == '2005' |  RollYr == '2006' |  RollYr == '2007' |  RollYr == '2008' | RollYr == '2009')       

test.years <- appraisal.data %>% filter(RollYr == '2010' | RollYr == '2011' | RollYr == '2012' | RollYr == '2013' | RollYr == '2014')   

 
totalOldYears <- merge(total.no.years,old.years ,by="PIN")   

totalNewYears <- merge(total.no.years, test.years, by="PIN")

```


### Creating the CSV Files

The following files we used in our modeling.
```{r}
total.no.years <- read.csv("finalDataNoYears.csv")
all.data <- read.csv('dataYears13to17.csv')
neighborhood.all.data <- read.csv("neighborhoodAllData.csv")
totalOldYears <- read_csv("totalOldYears.csv")
totalNewYears <- read_csv("totalNewYears.csv")
zoneFar <- read_csv("zoneFar.csv")
zoneFarTwo <- read_csv("zoneFar.csv")
colnames(zoneFar)[1] <- "Existing_Z"
```

### Split data into Residential, Commercial, Mixed Commercial + Residential, and Industrial Zoning

Since there are multiple types of properties in Seattle, we decided to create models that would reflect each type of property based on the zones that they have. 
```{r}
residential <- neighborhood.all.data %>% filter (ZONING == 'RSL/TC'| ZONING == 'SM/R-65'| ZONING == 'HR'| ZONING == 'SF 5000' | ZONING == 'LR3 PUD' | ZONING == 'LR3')
mixedCommercialRes <- neighborhood.all.data %>% filter(ZONING == 'SM-NR 55/75 2.0'| ZONING == 'SM-NR-85'| ZONING == 'MR-RC'| ZONING == 'LR1' | ZONING == 'LR2 RC' | ZONING == 'LR3 RC')
industrial <- neighborhood.all.data %>% filter(ZONING == 'IC-65'| ZONING == 'IC-45')
commercial <- neighborhood.all.data %>% filter(ZONING == 'NC3-40'| ZONING == 'NC3P-40' | ZONING == 'NC2P-40' | ZONING == 'NC2P-30' | ZONING == 'NC2-40' | ZONING == 'NC3-65' | ZONING == 'NC3-65' | ZONING == 'NC3P-85 5.75' | ZONING == 'NC3P-65' | ZONING == 'NC1-40' | ZONING == 'NC1-65' | ZONING == 'NC1-30' | ZONING == 'NC3P-85' | ZONING == 'C1-65' | ZONING == 'C2-65'| ZONING == 'C1-40' | ZONING == 'NC2-65' | ZONING == 'NC2P-65' | ZONING == 'NC1P-30' | ZONING == 'NC3-85' | ZONING == 'NC3-125' | ZONING == 'NC2P-65 4.0'| ZONING == 'NC3-65 2.0'| ZONING == 'NC2P-65 3.0' |  ZONING == 'NC3P-85 2.0' | ZONING == 'NC3P-85 2.0' | ZONING == 'NC3P-85 2.0'| ZONING == 'NC3P-65 2.0' | ZONING == 'NC3P-65 4.0' | ZONING == 'NC3-30' | ZONING == 'C2-30'| ZONING == 'NC2-30' | ZONING == 'NC1P-40' | ZONING == 'C2-40'| ZONING == 'NC3P-65 3.0'| ZONING == 'NC3P-85 4.75' | ZONING == 'NC3-85 4.75' | ZONING == 'NC3P-160' | ZONING == 'NC2P-65 0.75' | ZONING == 'C1-30' | ZONING == 'C1-40 0.75')

residential <- join(residential, zoneFar, by="Existing_Z", type="inner")
residential <- residential[residential$TotalVal<=10000000,]
mixedCommercialRes <- join(mixedCommercialRes, zoneFar, by="Existing_Z", type="inner")
industrial <- join(industrial, zoneFar, by="Existing_Z", type="inner")
commercial <- join(commercial, zoneFar, by="Existing_Z", type="inner")

colnames(zoneFarTwo)[1] <- "ZONING"

```


## Creating a model for residential properties
```{r, results = "hide", message=FALSE, warning = "hide", warning = FALSE}
split_proportion = 0.8
outcome <- residential %>% dplyr::select(TotalVal)
train_ind <- createDataPartition(outcome$TotalVal, p = split_proportion, list = FALSE)
mha_train <- residential[train_ind,] 
mha_test <- residential[-train_ind,] 

mha_test_x <- residential %>% dplyr::select(-TotalVal) 
mha_test_y <- residential %>% dplyr::select(TotalVal)

ctrl <- trainControl(method = "cv", number=5) 

# Train model
mha_model_lm <- train(TotalVal ~ RollYr + CurrentZoning + LOTSQFT + UV_NAME + FAR, 
                      data = residential, 
                      method = "lm", 
                      trControl=ctrl) 

mha_model_lm$finalModel
predict_mha_lm <- predict(mha_model_lm, mha_test_x)
postResample(predict_mha_lm, mha_test_y$TotalVal)
grid <- mha_test %>% gather_predictions(mha_model_lm)
residual <- resid(mha_model_lm)
```

#### Plotting the residuals
Based on these residuals, we concluded that our model had some limitations, and would not necessarily reflect the most accurate portrayal of predicted appraisal prices.
```{r}
plot(resid(mha_model_lm))
```


## Mixed Commercial/Residential Model
```{r, results = "hide", message=FALSE, warning = "hide", warning = FALSE}
## MIX COMMERCIAL RES ##
split_proportion = 0.8
outcome_MCR <- mixedCommercialRes %>% dplyr::select(TotalVal)
train_ind_MCR <- createDataPartition(outcome$TotalVal, p = split_proportion, list = FALSE)
MCR_train <- mixedCommercialRes[train_ind,] 
MCR_test <- mixedCommercialRes[-train_ind,] 

MCR_test_x <- mixedCommercialRes %>% dplyr::select(-TotalVal) 
MCR_test_y <- mixedCommercialRes %>% dplyr::select(TotalVal)

ctrl <- trainControl(method = "cv", number=5) 

# Train model
MCR_model_lm <- train(TotalVal ~ RollYr + CurrentZoning + LOTSQFT + UV_NAME + FAR, 
                      data = mixedCommercialRes, 
                      method = "lm", 
                      trControl=ctrl) 

MCR_model_lm$finalModel

predict_MCR_lm <- predict(MCR_model_lm, MCR_test_x)
postResample(predict_MCR_lm, MCR_test_y$TotalVal)
grid_MCR <- MCR_test %>% gather_predictions(MCR_model_lm)
residual_MCR <- resid(MCR_model_lm)
```

#### Plotting the residuals
```{r}
plot(resid(MCR_model_lm))
```
As this was our first introductory data science course, we did not have the capacity to improve our models, but recognize that some tweaking to improve our performance is necessary.

## Industrial Model
```{r, results = "hide", message=FALSE, warning = "hide", warning = FALSE}
split_proportion = 0.8
outcome_indus <- industrial %>% dplyr::select(TotalVal)
train_ind_indus <- createDataPartition(outcome$TotalVal, p = split_proportion, list = FALSE)
indus_train <- industrial[train_ind,] 
indus_test <- industrial[-train_ind,] 

indus_test_x <- industrial %>% dplyr::select(-TotalVal) 
indus_test_y <- industrial %>% dplyr::select(TotalVal)

ctrl <- trainControl(method = "cv", number=5) 

# Train model
indus_model_lm <- train(TotalVal ~ RollYr + CurrentZoning + LOTSQFT + UV_NAME + FAR, 
                        data = industrial, 
                        method = "lm", 
                        trControl=ctrl) 

indus_model_lm$finalModel

predict_indus_lm <- predict(indus_model_lm, indus_test_x)
postResample(predict_indus_lm, indus_test_y$TotalVal)
grid_indus <- indus_test %>% gather_predictions(indus_model_lm)
residual_indus <- resid(indus_model_lm)
```

#### Plotting the residuals
```{r}
plot(resid(indus_model_lm))
```


## Commercial Property Model
```{r, results = "hide", message=FALSE, warning = "hide", warning = FALSE}
split_proportion = 0.8
outcome_com <- commercial %>% dplyr::select(TotalVal)
train_ind_com <- createDataPartition(outcome$TotalVal, p = split_proportion, list = FALSE)
com_train <- commercial[train_ind,] 
com_test <- commercial[-train_ind,] 

com_test_x <- commercial %>% dplyr::select(-TotalVal) 
com_test_y <- commercial %>% dplyr::select(TotalVal)

ctrl <- trainControl(method = "cv", number=5) 

# Train model
com_model_lm <- train(TotalVal ~ RollYr + CurrentZoning + LOTSQFT + UV_NAME + FAR, 
                      data = commercial, 
                      method = "lm", 
                      trControl=ctrl) 

com_model_lm$finalModel

predict_com_lm <- predict(com_model_lm, com_test_x)
postResample(predict_com_lm, com_test_y$TotalVal)
grid_com <- com_test %>% gather_predictions(com_model_lm)
residual_com <- resid(com_model_lm)
```

```{r}
# residuals 
plot(resid(com_model_lm))
```

# Testing Validity of Model
We conducted training the predictive model with past data (2000-2010) and testing it with new data (2013-2017) to determine if our model had any validity when predicting new unseen years, as our goal was to forecast the future

The data that we used was too large to push up to Github, but the code can be viewed below. From our residual plot and qqnorm plot, our model did not perform very well.

```{r eval=FALSE}
oldYears <- old.years 
newYears <- test.years

na.omit(oldYears)
na.omit(newYears)

newYears_test <- newYears
newYears_test_x <- newYears %>% dplyr::select(-TotalVal) 
newYears_test_y <- newYears %>% dplyr::select(TotalVal)

ctrl <- trainControl(method = "cv", number=5) 

oldYears_model_lm <- train(TotalVal ~ RollYr + CurrentZoning + LOTSQFT, 
                           data = oldYears, 
                           method = "lm", 
                           trControl=ctrl) 

oldYears_model_lm$finalModel

predict_newYears_lm <- predict(oldYears_model_lm, newYears_test_x)

postResample(predict_newYears_lm, newYears_test_y$TotalVal)
grid <- newYears_test %>% gather_predictions(oldYears_model_lm)
varImp(oldYears_model_lm)

ggplot(newYears_test, aes(RollYr, TotalVal, color = 'red')) +  geom_point() + geom_line(data = grid, aes(y = pred ))
resid(oldYears_model_lm) 
plot(resid(oldYears_model_lm)) #A density plot
qqnorm(resid(oldYears_model_lm)) # A quantile normal plot - good for checking normality
```

## Predicting Residential Appraisal Values in 2018

#### With the Rezone
```{r eval=FALSE}
reZonePrediction <- function() {
  residentialfuture <- residential %>% filter(RollYr == '2017')
  residential2017 <-residential %>% filter(RollYr == '2017')
  residentialfuture$RollYr <- 2018
  residentialfuture$MHA_ZONING <- gsub("M1", "", residentialfuture$MHA_ZONING)
  residentialfuture$MHA_ZONING <- gsub("[(M)]", "", residentialfuture$MHA_ZONING)
  residentialfuture$MHA_ZONING <- gsub("[()]", "", residentialfuture$MHA_ZONING)
  
  residentialfuture$ZONING <- residentialfuture$MHA_ZONING 
  
  totalfuture <- rbind(residentialfuture, residential)
  mha_test_x <- totalfuture %>% dplyr::select(-TotalVal) 
  mha_test_y <- totalfuture %>% dplyr::select(TotalVal)
  
  predict_mha_lm <- predict(mha_model_lm, mha_test_x)
  postResample(predict_mha_lm, mha_test_y$TotalVal)
  grid <- totalfuture %>% gather_predictions(mha_model_lm)
  return(grid)
}
```

#### Without the Rezone
```{r eval=FALSE}
noRezonePredictionRes <- function() {
  residentialNoZone <- residential %>% filter(RollYr == '2017')
  residentialNoZone$RollYr <- 2018
  residentialNoZone$MHA_ZONING <- gsub("M1", "", residentialNoZone$MHA_ZONING)
  residentialNoZone$MHA_ZONING <- gsub("[(M)]", "", residentialNoZone$MHA_ZONING)
  residentialNoZone$MHA_ZONING <- gsub("[()]", "", residentialNoZone$MHA_ZONING)  
  
  mha_test_xResNoZone <- residentialNoZone %>% dplyr::select(-TotalVal) 
  mha_test_yResNoZone <- residentialNoZone %>% dplyr::select(TotalVal)
  
  predict_mha_lmResNoZone <- predict(mha_model_lm, mha_test_xResNoZone)
  postResample(predict_mha_lmResNoZone, mha_test_yResNoZone$TotalVal)
  gridResNoZone <- residentialNoZone %>% gather_predictions(mha_model_lm)
  
  gridResNoZone$TotalVal <- gridResNoZone$pred
  gridResNoZone <- gridResNoZone[,2:25]
  totalResNoZone <- rbind(gridResNoZone, residential)
  return(totalResNoZone)
}
```

## Mixed Commercial and Residential Predictions

#### With the Rezone
```{r eval=FALSE}
mixedRezone <- function() {
  mixRezone <-mixedCommercialRes %>% filter(RollYr == '2017')
  mixRezone$RollYr <- 2018
  mixRezone$MHA_ZONING <- gsub("M1", "", mixRezone$MHA_ZONING)
  mixRezone$MHA_ZONING <- gsub("[(M)]", "", mixRezone$MHA_ZONING)
  mixRezone$MHA_ZONING <- gsub("[()]", "", mixRezone$MHA_ZONING)
  
  mixRezone$Existing_Z <- mixRezone$MHA_ZONING 
  mha_test_xRezone <- mixRezone %>% dplyr::select(-TotalVal) 
  mha_test_yRezone <- mixRezone %>% dplyr::select(TotalVal)
  
  predict_mha_lmRezone <- predict(MCR_model_lm, mha_test_xRezone)
  postResample(predict_mha_lmRezone, mha_test_yRezone$TotalVal)
  gridRezone <- mixRezone %>% gather_predictions(MCR_model_lm)
  
  gridRezone$TotalVal <- gridRezone$pred
  gridRezone <- gridRezone[,2:25]
  totalMixRezone <- rbind(gridRezone, mixedCommercialRes)
  return(totalMixRezone)
}
```

#### Without the Rezone
```{r eval=FALSE}
mixedNoRezone <- function() {
  mixNoZone <- mixedCommercialRes %>% filter(RollYr == '2017')
  mixNoZone$RollYr <- 2018
  mixNoZone$MHA_ZONING <- gsub("M1", "", mixNoZone$MHA_ZONING)
  mixNoZone$MHA_ZONING <- gsub("[(M)]", "", mixNoZone$MHA_ZONING)
  mixNoZone$MHA_ZONING <- gsub("[()]", "", mixNoZone$MHA_ZONING)  
  
  mha_test_xMixNoZone <- mixNoZone %>% dplyr::select(-TotalVal) 
  mha_test_yMixNoZone <- mixNoZone %>% dplyr::select(TotalVal)
  
  predict_mha_lmMixNoZone <- predict(MCR_model_lm, mha_test_xMixNoZone)
  postResample(predict_mha_lmMixNoZone, mha_test_yMixNoZone$TotalVal)
  gridMixNoZone <- mixNoZone %>% gather_predictions(MCR_model_lm)
  
  gridMixNoZone$TotalVal <- gridMixNoZone$pred
  gridMixNoZoned <- gridMixNoZone[,2:25]
  totalMixNoZone <- rbind(gridMixNoZoned, mixedCommercialRes)
  return(totalMixNoZone)
}
```
## Commercial Predictions

#### With the Rezone
```{r eval=FALSE}
commercialRezone <- function() {
  comRezone <-commercial %>% filter(RollYr == '2017')
  comRezone$RollYr <- 2018
  comRezone$MHA_ZONING <- gsub("M1", "", comRezone$MHA_ZONING)
  comRezone$MHA_ZONING <- gsub("[(M)]", "", comRezone$MHA_ZONING)
  comRezone$MHA_ZONING <- gsub("[()]", "", comRezone$MHA_ZONING)
  
  comRezone$ZONING <- comRezone$MHA_ZONING 
  mha_test_xComRezone <- comRezone %>% dplyr::select(-TotalVal) 
  mha_test_ComRezone <- comRezone %>% dplyr::select(TotalVal)
  
  predict_mha_lmComRezone <- predict(com_model_lm, mha_test_xComRezone)
  postResample(predict_mha_lmComRezone, mha_test_ComRezone$TotalVal)
  gridComRezone <- comRezone %>% gather_predictions(com_model_lm)
  
  gridComRezone$TotalVal <- gridComRezone$pred
  gridComRezone <- gridComRezone[,2:25]
  totalComRezone <- rbind(gridComRezone, commercial)
  return(totalComRezone)
}
```
#### Without the Rezone
```{r eval=FALSE}
commercialNoRezone <- function() {
  commercialNoZone <- commercial %>% filter(RollYr == '2017')
  commercialNoZone$RollYr <- 2018
  commercialNoZone$MHA_ZONING <- gsub("M1", "", commercialNoZone$MHA_ZONING)
  commercialNoZone$MHA_ZONING <- gsub("[(M)]", "", commercialNoZone$MHA_ZONING)
  commercialNoZone$MHA_ZONING <- gsub("[()]", "", commercialNoZone$MHA_ZONING)  
  
  mha_test_xComNoZone <- commercialNoZone %>% dplyr::select(-TotalVal) 
  mha_test_yComNoZone <- commercialNoZone %>% dplyr::select(TotalVal)
  
  predict_mha_lmComNoZone <- predict(com_model_lm, mha_test_xComNoZone)
  postResample(predict_mha_lmComNoZone, mha_test_yComNoZone$TotalVal)
  gridComNoZone <- commercialNoZone %>% gather_predictions(com_model_lm)
  
  gridComNoZone$TotalVal <- gridComNoZone$pred
  gridComNoZoned <- gridComNoZone[,2:25]
  totalComNoZone <- rbind(gridComNoZoned, commercial)
  return(totalComNoZone)
}
```
## Industrial Predictions

#### With the Rezone
```{r eval=FALSE}
industrialRezone <- function() {
  indRezone <-industrial %>% filter(RollYr == '2017')
  indRezone$RollYr <- 2018
  indRezone$MHA_ZONING <- gsub("M1", "", indRezone$MHA_ZONING)
  indRezone$MHA_ZONING <- gsub("[(M)]", "", indRezone$MHA_ZONING)
  indRezone$MHA_ZONING <- gsub("[()]", "", indRezone$MHA_ZONING)
  
  indRezone$ZONING <- indRezone$MHA_ZONING 
  mha_test_xIndRezone <- indRezone %>% dplyr::select(-TotalVal) 
  mha_test_yIndRezone <- indRezone %>% dplyr::select(TotalVal)
  
  predict_mha_lmIndRezone <- predict(indus_model_lm, mha_test_xIndRezone)
  postResample(predict_mha_lmIndRezone, mha_test_yIndRezone$TotalVal)
  gridIndRezone <- indRezone %>% gather_predictions(indus_model_lm)
  
  gridIndRezone$TotalVal <- gridIndRezone$pred
  gridIndRezone <- gridIndRezone[,2:25]
  totalIndRezone <- rbind(gridIndRezone, industrial)
  return(totalIndRezone)
}

```
#### Without the Rezone
```{r eval=FALSE}
industrialNoRezone <- function() {
  industrialNoZone <- industrial %>% filter(RollYr == '2017')
  industrialNoZone$RollYr <- 2018
  industrialNoZone$MHA_ZONING <- gsub("M1", "", industrialNoZone$MHA_ZONING)
  industrialNoZone$MHA_ZONING <- gsub("[(M)]", "", industrialNoZone$MHA_ZONING)
  industrialNoZone$MHA_ZONING <- gsub("[()]", "", industrialNoZone$MHA_ZONING)  
  
  mha_test_xIndNoZone <- industrialNoZone %>% dplyr::select(-TotalVal) 
  mha_test_yIndNoZone <- industrialNoZone %>% dplyr::select(TotalVal)
  
  predict_mha_lmIndNoZone <- predict(indus_model_lm, mha_test_xIndNoZone)
  postResample(predict_mha_lmIndNoZone, mha_test_yIndNoZone$TotalVal)
  gridIndNoZone <- industrialNoZone %>% gather_predictions(indus_model_lm)
  
  gridIndNoZone$TotalVal <- gridIndNoZone$pred
  gridIndNoZone <- gridIndNoZone[,2:25]
  totalIndNoZone <- rbind(gridIndNoZone, industrial)
  return(totalIndNoZone)
}
```

## Predicting Neighborhood Prices Until 2022
For this portion, we did not use the model we created. Instead, we utilized a forecasting library called Prophet.
```{r eval=FALSE}
HomePrices <- read_csv("Neighborhood_Zhvi_AllHomes.csv")
all.homes <- HomePrices %>% filter(City == 'Seattle')

PredictNeighborhoodSalePrice <- function(neighborhood) {
  data <- all.homes %>% filter(RegionName == neighborhood)
  getCol <- data[,8:266]
  names <- colnames(getCol)
  prices <- as.numeric(getCol[1,])
  newdata <- data.frame(names,prices)
  colnames(newdata) <- c("ds", "y")
  newdata$ds <- as.Date(paste(newdata$ds,"-01",sep=""))
  
  model <- prophet(newdata)
  future <- make_future_dataframe(model, periods = 60, freq = "month")
  forecast <- predict(model, future) %>% select(ds, yhat) 
  forecast$ds <- as.Date(forecast$ds)
  
  join.data <- left_join(forecast, newdata, by = "ds")
  colnames(join.data) <- c("Date", "Predicted", "Actual")
  return(join.data)
}
```

## Predicting Single Address Value in 2018
```{r eval=FALSE}
PredictAddressSalePrice <- function(address) {
address <- toupper(address)
data <- neighborhood.all.data %>% filter(ADDR_FULL == address)
if (data$ZONING == 'RSL/TC'| data$ZONING == 'SM/R-65'| data$ZONING == 'HR'| data$ZONING == 'SF 5000' | data$ZONING == 'LR3 PUD' | data$ZONING == 'LR3' ) {
model <- mha_model_lm
} else if (data$ZONING == 'SM-NR 55/75 2.0'| data$ZONING == 'SM-NR-85'| data$ZONING == 'MR-RC'| data$ZONING == 'LR1' | data$ZONING == 'LR2 RC' | data$ZONING == 'LR3 RC') {
model <- MCR_model_lm
} elseif (data$ZONING == 'IC-65'| data$ZONING == 'IC-45'){
model <- indus_model_lm
} else if (data$ZONING == 'NC3-40'| data$ZONING == 'NC3P-40' | data$ZONING == 'NC2P-40' | data$ZONING == 'NC2P-30' | data$ZONING == 'NC2-40' | data$ZONING == 'NC3-65'
| data$ZONING == 'NC3-65' | data$ZONING == 'NC3P-85 5.75' | data$ZONING == 'NC3P-65' | data$ZONING == 'NC1-40' | data$ZONING == 'NC1-65' | data$ZONING == 'NC1-30' |
data$ZONING == 'NC3P-85' | data$ZONING == 'C1-65' | data$ZONING == 'C2-65'| data$ZONING == 'C1-40' | data$ZONING == 'NC2-65' | data$ZONING == 'NC2P-65' | data$ZONING == 'NC1P-30' 
| data$ZONING == 'NC3-85' | data$ZONING == 'NC3-125' | data$ZONING == 'NC2P-65 4.0'| data$ZONING == 'NC3-65 2.0'| data$ZONING == 'NC2P-65 3.0' |data$ZONING == 'NC3P-85 2.0' 
| data$ZONING == 'NC3P-85 2.0' | data$ZONING == 'NC3P-85 2.0'| data$ZONING == 'NC3P-65 2.0' | data$ZONING == 'NC3P-65 4.0' | data$ZONING == 'NC3-30' | data$ZONING == 'C2-30'
| data$ZONING == 'NC2-30' | data$ZONING == 'NC1P-40' | data$ZONING == 'C2-40'| data$ZONING == 'NC3P-65 3.0'| data$ZONING == 'NC3P-85 4.75' | data$ZONING == 'NC3-85 4.75' 
| data$ZONING == 'NC3P-160' | data$ZONING == 'NC2P-65 0.75' | data$ZONING == 'C1-30' | data$ZONING == 'C1-40 0.75'){
model <- com_model_lm
}

data <- data %>% filter(ADDR_FULL == address)
data <- join(data, zoneFar, by="Existing_Z", type="inner")  
yr2017 <- data %>% filter(RollYr == '2017')
yr2017$RollYr <- 2018
yr2017$ZONING <- yr2017$MHA_ZONING 
future <- rbind(data, yr2017)
future$ZONING <- gsub("M1", "", future$ZONING)
future$ZONING <- gsub("[(M)]", "", future$ZONING)
future$ZONING <- gsub("[()]", "", future$ZONING)

mha_test_x <- future %>% dplyr::select(-TotalVal) 
mha_test_y <- future %>% dplyr::select(TotalVal)

predict_mha_lm <- predict(model, mha_test_x)
postResample(predict_mha_lm, mha_test_y$TotalVal)
grid <- future %>% gather_predictions(model)
grid$RollYr <- as.numeric(grid$RollYr)
return(grid)
}

```